---
title: "SIBSSD"
output: html_document
---
1: Randomly generate a set of balanced N*m SSDs as initial particles
2: Evaluate objective function value of each SSD
3: Initialize the LB for all SSDs
4: Initialize the GB
5: while not converge do
6:   For each SSD, perform the MIX operation
7:   For each SSD, perform the MOVE operation
8:   Evaluate objective function value of each SSD
9:   Update the LB for all SSDs
10:  Update the GB
11: end while

#how to read rmd
```{r}
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

#read functions
```{r}
Sys.setlocale('LC_ALL','C')
source_rmd("D:/statisic/Master_thesis/SIBSSD/SIBSSD_functions.Rmd")
```

#main function
```{r}
SIBSSD <- function(particle, N, m, qLB, qGB, iteration, early.break = 100){
  
  #1: Randomly generate a set of balanced N*m SSDs as initial particles
  SIBSSD.list <- list()
  for(i in 1:particle){
    SIBSSD.list[[i]] <- generateSSD(N = N, m = m)  
  }
  
  #2: Evaluate objective function value of each SSD
  Es2.value <- sapply(SIBSSD.list,evaluateEs2)
  
  #3: Initialize the LB for all SSDs
  LB <- list()
  for(i in 1:particle){
    LB[[i]] <- list(design = SIBSSD.list[[i]], value = Es2.value[i])   
  }
  
  #4: Initialize the GB
  GB <- LB[[1]]
  for(i in 1:particle){
    if(LB[[i]]$value < GB$value)
    GB <- LB[[i]]   
  }
  
  #record the GB value
  record <- GB$value
  
  #5: while not converge do
  progress <- 0                            #index for print when make progress and early break
  break.index <- 1
  for(i in 1:iteration){
    
    #deal with early break and print when make progress
    if((i - break.index) >= early.break){
      break  
    }else if(progress == 1){
      print(GB)
      progress <- 0
      break.index <- i
    }

    
    
    #6: For each SSD, perform the MIX operation 
    mixw <- mixOperation(particle = particle, SIBSSD.list = SIBSSD.list, LB = LB,GB = GB, qLB = qLB, qGB = qGB)
    
    ####
    # mixLB.tem <- numeric(particle)
    # mixGB.tem <- numeric(particle)
    # for(i in 1:particle){
    #   mixLB.tem[i] <- mixw$mixwLB[[i]]$value
    #   mixGB.tem[i] <- mixw$mixwGB[[i]]$value  
    # }
    # print(mixLB.tem)
    # print(mixGB.tem)
    # 
    # print(mixw$mixwLB[[1]]$design)
    # print(mixw$mixwGB[[1]]$design)
    ####

    #7: For each SSD, perform the MOVE operation
    SIBSSD.list <- moveOperation(particle = particle,
                                 SIBSSD.list = SIBSSD.list, 
                                 mixwLB = mixw$mixwLB, 
                                 mixwGB = mixw$mixwGB, 
                                 qLB = qLB, 
                                 qGB = qGB)
    
    #9: Update the LB for all SSDs
    Es2.value <- sapply(SIBSSD.list,evaluateEs2)

    for(j in 1:particle){
      if(Es2.value[j] < LB[[j]]$value){
        LB[[j]] <- list(design = SIBSSD.list[[j]], value = Es2.value[j])  
      }
    }
    
    #10: Update the GB
    if(min(Es2.value) < GB$value){
      GB <- LB[[which.min(Es2.value)]] 
      progress <- 1
    }
  
  record <- c(record,GB$value)

  #11: end while
  }
  return(list(GB,record))  
}
```

#for test
```{r}
SIBSSD_test <- function(test.value, particle, N, m, qLB, qGB, iteration, early.break = 100){
  
  #1: Randomly generate a set of balanced N*m SSDs as initial particles
  SIBSSD.list <- list()
  for(i in 1:particle){
    SIBSSD.list[[i]] <- generateSSD(N = N, m = m)  
  }
  
  #2: Evaluate objective function value of each SSD
  Es2.value <- sapply(SIBSSD.list,evaluateEs2)
  
  #3: Initialize the LB for all SSDs
  LB <- list()
  for(i in 1:particle){
    LB[[i]] <- list(design = SIBSSD.list[[i]], value = Es2.value[i])   
  }
  
  #4: Initialize the GB
  GB <- LB[[1]]
  for(i in 1:particle){
    if(LB[[i]]$value < GB$value)
    GB <- LB[[i]]   
  }
  
  #record the GB value
  record <- GB$value
  
  #5: while not converge do
  progress <- 0                            #index for print when make progress and early break
  break.index <- 1
  for(i in 1:iteration){
    if(GB$value <= test.value){
      break;
    }
    
    #deal with early break and print when make progress
    if((i - break.index) >= early.break){
      break  
    }else if(progress == 1){
      print(GB)
      progress <- 0
      break.index <- i
    }

    
    
    #6: For each SSD, perform the MIX operation 
    mixw <- mixOperation(particle = particle, SIBSSD.list = SIBSSD.list, LB = LB,GB = GB, qLB = qLB, qGB = qGB)
    


    #7: For each SSD, perform the MOVE operation
    SIBSSD.list <- moveOperation(particle = particle,
                                 SIBSSD.list = SIBSSD.list, 
                                 mixwLB = mixw$mixwLB, 
                                 mixwGB = mixw$mixwGB, 
                                 qLB = qLB, 
                                 qGB = qGB)
    
    #9: Update the LB for all SSDs
    Es2.value <- sapply(SIBSSD.list,evaluateEs2)

    for(j in 1:particle){
      if(Es2.value[j] < LB[[j]]$value){
        LB[[j]] <- list(design = SIBSSD.list[[j]], value = Es2.value[j])  
      }
    }
    
    #10: Update the GB
    if(min(Es2.value) < GB$value){
      GB <- LB[[which.min(Es2.value)]] 
      progress <- 1
    }
  
  record <- c(record,GB$value)

  #11: end while
  }
  return(list(GB,record))  
}
```


#test
```{r}
N <- 6
m <- 10
qLB <- round(m/4)
qGB <- round(m/6)
SIBSSD(particle = 5, N = N, m = m, qLB = qLB, qGB = qGB, iteration = 10, early.break = 100)
```

```{r}
library(tictoc)
tic()
N <- 14
m <- 23
qLB <- round(m/3)
qGB <- round(m/6)
SIBSSD(particle = 100, N = N, m = m, qLB = qLB, qGB = qGB, iteration = 150,early.break = 100)
toc()
```

time 10480.03 sec elapsed
```{r}
library(tictoc)
tic()
N <- 10
m <- 18
qLB <- round(m/3)
qGB <- round(m/6)
SIBSSD(particle = 500, N = N, m = m, qLB = qLB, qGB = qGB, iteration = 500,early.break = 100)
toc()
```

time 1564.22 sec elapsed
```{r}
library(tictoc)
tic()
N <- 10
m <- 18
qLB <- round(m/3)
qGB <- round(m/6)
SIBSSD_test(test.value = 5.8824,particle = 500, N = N, m = m, qLB = qLB, qGB = qGB, iteration = 500,early.break = 100)
toc()
```


