---
title: "mSIBSSD"
output: html_document
---
1: Randomly generate a set of balanced (n1*n2)*(m1+m2) multistratum SSDs as initial particles
2: Evaluate objective function value of each SSD
3: Initialize the LB for all SSDs
4: Initialize the GB
5: while not converge do
6:   For each SSD, perform the MIX operation
7:   For each SSD, perform the MOVE operation
8:   Evaluate objective function value of each SSD
9:   Update the LB for all SSDs
10:  Update the GB
11: end while

```{r}
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

#read functions
```{r}
Sys.setlocale('LC_ALL','C')
source_rmd("D:/statisic/Master_thesis/spilt-plot_MSIBSSD_Df/MSIBSSD_DF_functions.Rmd")
```

```{r}
m1 = 8
m2 = 8
n1 = 6
n2 = 6
qLB = 4
qGB = 3
mSSD <- generateMSSD(m1 = m1, m2 = m2, n1 = n1, n2 = n2)
Dcriterion(mSSD = table1, f = 2, m1 = m1, m2 = m2, n1 = n1, n2 = n2)

```

```{r}
table1 <- read.csv("D:/statisic/Master_thesis/MSIBSSD_DF/table1.csv",  header = FALSE)
table1 <- as.matrix(table1)

```
```{r}
m1 = 8
m2 = 8
n1 = 6
n2 = 6
Dcriterion(mSSD = table1, f = 2, m1 = m1, m2 = m2, n1 = n1, n2 = n2)
Dcriterion(mSSD = table1, f = 3, m1 = m1, m2 = m2, n1 = n1, n2 = n2)
Dcriterion(mSSD = table1, f = 4, m1 = m1, m2 = m2, n1 = n1, n2 = n2)
Dcriterion(mSSD = table1, f = 5, m1 = m1, m2 = m2, n1 = n1, n2 = n2)
```

```{r}
mSIBSSD <- function(particle,f, m1, m2, n1, n2, qLB, qGB, w.ratio, iteration, early.break = 100){
  
  #1: Randomly generate a set of balanced N*m SSDs as initial particles
  mSIBSSD.list <- list()
  for(i in 1:particle){
    mSIBSSD.list[[i]] <- generateMSSD(m1 = m1, m2 = m2, n1 = n1, n2 = n2)  
  }
  
  #2: Evaluate objective function value of each SSD
  Df.value <- numeric(particle)
  for(j in 1:particle){
    Df.value[j] <- Dcriterion(mSSD = mSIBSSD.list[[j]], f = f,m1 = m1, m2 = m2, n1 = n1,n2 = n2)  
  }
  
  #3: Initialize the LB for all SSDs
  LB <- list()
  for(i in 1:particle){
    LB[[i]] <- list(design = mSIBSSD.list[[i]], value = Df.value[i])   
  }
  
  #4: Initialize the GB
  GB <- LB[[1]]
  for(i in 1:particle){
    if(LB[[i]]$value > GB$value)
    GB <- LB[[i]]   
  }
  
  #record the GB value
  record <- GB$value
  
  #5: while not converge do
  progress <- 0                            #index for print when make progress and early break
  break.index <- 1
  for(i in 1:iteration){
    
    #deal with early break and print when make progress
    if((i - break.index) >= early.break){
      break  
    }else if(progress == 1){
      print(GB)
      progress <- 0
      break.index <- i
    }

    
    
    #6: For each SSD, perform the MIX operation 
    mixw <- mixOperation(particle = particle,mSIBSSD.list = mSIBSSD.list, w.ratio = w.ratio, LB = LB,GB = GB, qLB = qLB, qGB = qGB)
    
    ####
    # mixLB.tem <- numeric(particle)
    # mixGB.tem <- numeric(particle)
    # for(i in 1:particle){
    #   mixLB.tem[i] <- mixw$mixwLB[[i]]$value
    #   mixGB.tem[i] <- mixw$mixwGB[[i]]$value  
    # }
    # print(mixLB.tem)
    # print(mixGB.tem)
    # 
    # print(mixw$mixwLB[[1]]$design)
    # print(mixw$mixwGB[[1]]$design)
    ####

    #7: For each SSD, perform the MOVE operation
    mSIBSSD.list <- moveOperation(particle = particle,
                                  mSIBSSD.list = mSIBSSD.list,
                                  w.ratio = w.ratio,
                                  mixwLB = mixw$mixwLB, 
                                  mixwGB = mixw$mixwGB, 
                                  qLB = qLB, 
                                  qGB = qGB)
    
    #9: Update the LB for all SSDs
    Df.value <- numeric(particle)
    for(j in 1:particle){
      Df.value[j] <- Dcriterion(mSSD = mSIBSSD.list[[j]], f = f,m1 = m1, m2 = m2, n1 = n1,n2 = n2)  
    }

    for(j in 1:particle){
      if(Df.value[j] > LB[[j]]$value){
        LB[[j]] <- list(design = mSIBSSD.list[[j]], value = Df.value[j])  
      }
    }
    
    #10: Update the GB
    if(max(Df.value) > GB$value){
      GB <- LB[[which.max(Df.value)]] 
      progress <- 1
    }
  
  record <- c(record,GB$value)

  #11: end while
  }
  return(list(GB,record))  
}
```
$value
[1] 10.79186

22057.61 sec elapsed
```{r}
particle = 500
m1 = 8
m2 = 8
n1 = 6
n2 = 6
f = 2
qLB = 4
qGB = 3
w.ratio = 0.2
library(tictoc)
tic()
test <- mSIBSSD(particle = particle,f = f, m1 = m1, m2 = m2, n1 = n1, n2 = n2, qLB = qLB, qGB = qGB, w.ratio = w.ratio, iteration = 500, early.break = 100)
toc()
```

```{r}
Dcriterion(test[[1]]$design,f=2,m1=m1,m2=m2,n1,n1)
```

