---
title: "Find_alpha"
output: html_document
---
# examples

```{r}
x<-c(-1,-.5,0,.5,1)
xpri<-cbind(1,x)
xpot<-x^2
alpha<-as.matrix(lm(xpot~x)$coefficients)
R<-xpot-xpri%*%alpha
max(R)-min(R)
z1<-R/(max(R)-min(R))
z1
alpha
```
#Two factor
```{r}
x <- matrix(c(1,1,-1,-1,1,-1,1,-1),4,2)
m <- ncol(x)
xpri<-cbind(1,x)
index.matrix <- combn(m,2)
p2 <- ncol(index.matrix)
xpot <- matrix(0,nrow(x),choose(m,2))
for(i in 1:p2){
  xpot[,i] <- x[,index.matrix[1,i]] * x[,index.matrix[2,i]]
}
alpha<-as.matrix(lm(xpot~x)$coefficients)
R<-xpot-xpri%*%alpha
x
max(R)-min(R)
z1<-R/(max(R)-min(R))
z1
alpha
```
#Three factor
```{r}
x <- matrix(0,2^3,3)
l <- 1
for(i in c(1,-1)){
  for(j in c(1,-1)){
    for(k in c(1,-1)){
      x[l,] <- c(i,j,k)
      l <- l + 1 
    }
  }
}
x
m <- ncol(x)
xpri<-cbind(1,x)
index.matrix <- combn(m,2)
p2 <- ncol(index.matrix)
xpot <- matrix(0,nrow(x),choose(m,2))
for(i in 1:p2){
  xpot[,i] <- x[,index.matrix[1,i]] * x[,index.matrix[2,i]]
}
alpha<-as.matrix(lm(xpot~x)$coefficients)
R<-xpot-xpri%*%alpha
max(R)-min(R)
z1<-R/(max(R)-min(R))
z1
alpha
```

#four factor
```{r}
x <- matrix(0,2^4,4)
l <- 1
for(i in c(1,-1)){
  for(j in c(1,-1)){
    for(k in c(1,-1)){
      for(m in c(1,-1)){
         x[l,] <- c(i,j,k,m)
         l <- l + 1   
      }
     
    }
  }
}
x
m <- ncol(x)
xpri<-cbind(1,x)
index.matrix <- combn(m,2)
p2 <- ncol(index.matrix)
xpot <- matrix(0,nrow(x),choose(m,2))
for(i in 1:p2){
  xpot[,i] <- x[,index.matrix[1,i]] * x[,index.matrix[2,i]]
}
alpha<-as.matrix(lm(xpot~x)$coefficients)
R<-xpot-xpri%*%alpha
max(R)-min(R)
z1<-R/(max(R)-min(R))
z1
alpha
```

# all terms except the intercept are potential terms(24,30)
```{r}
xpri <- rep(1,24)
xpot <- A
alpha<-as.matrix(lm(xpot~xpri-1)$coefficients)
R<-xpot-xpri%*%alpha
max(R)-min(R)
z1<-R/(max(R)-min(R))
z1
alpha
```
# we assume that the first p1−1
factors are known to be active and the remaining p2 factors are to be screened(12,16)
```{r}
n <- 2^15
m <- 15
xpri <- matrix(0,n,m)
# rep(rep(c(1,-1),each = n/2),1)
# rep(rep(c(1,-1),each = n/4),2)
for(i in 1:m){
  xpri[,i] <- rep(rep(c(1,-1),each = n/(2^i)),2^(i-1))
}
xpot <- xpri
xpri <- cbind(1,xpri)
alpha<-as.matrix(lm(xpot~xpri-1)$coefficients)
R<-xpot-xpri%*%alpha
apply(R,2,max) - apply(R,2,min)
R/(max(R)-min(R))
```

########################################
```{r}
SSD <- as.matrix(read.csv("D:/statisic/Master_thesis/SIBSSD_BayesianD/24x30A.csv",header = F))
```

# all terms except the intercept are potential terms
```{r}
find_alpha_R <- function(m){
  random.row <- sample.int(2^m,10000) #choose 10000 times to approximate true value

  index <- c(1,-1)
  inf.matrix <- c()
  # rep(rep(c(1,-1),each = n/2),1)
  # rep(rep(c(1,-1),each = n/4),2)
  #for(i in 1:n){
  for(i in random.row){
    tem.matrix <- numeric(m)+1
    tem <- i
    for(j in 1:m){
      if(tem == 0){
        break
      }else{
        tem <- tem/2
        quotient <- floor(tem)
        remainder <- tem - quotient 
        tem.matrix[m-j+1] <- index[(remainder != 0)+1]
        tem <- quotient 
      }
      
    }
    
    inf.matrix <- rbind(inf.matrix, tem.matrix)
  }
  
  xpri <- matrix(1,nrow = nrow(inf.matrix),1)
  xpot <- inf.matrix
  #xpri <- cbind(1,xpri)
  #solve(t(xpri) %*% xpri) %*% t(xpri) %*% xpot
  alpha <- as.matrix(lm(xpot~xpri-1)$coefficients)
  #xpri <- cbind(1,xpri)
  R <- xpot-xpri%*%alpha
  R.range <- apply(R,2,max) - apply(R,2,min)
  #print(alpha)
  #print(R)
 
  
  return(list(alpha = alpha, R.range = R.range))      
}
```
```{r}
for(i in 1:5){
  alpha_R <- find_alpha_R(30)
  print(alpha_R)
}
```
```{r}
SSD
primary <- matrix(1, nrow = nrow(SSD))
potential <- SSD
alpha <- alpha_R$alpha
R.range <- alpha_R$R.range



xpot<-potential
R<-xpot-primary%*%matrix(alpha,1) 
potential.adj <- c()
for(i in 1:length(R.range)){
  z<-R[,i]/R.range[i]
  potential.adj<-cbind(potential.adj,z)  
}
potential.adj
```

# Evaluate Bayesiand value
```{r}
evaluateBayesianD <- function(SSD){
  tau <- sqrt(5)
  m <- ncol(SSD)
  
  #primary
  primary <- matrix(1,nrow = nrow(SSD),1)
  p1 <- ncol(primary)
  
  #potential
  potential <- SSD
  p2 <- ncol(potential)
  potential.adj <- potential / 2   #we can see the reson above
  
  
  
  x <- as.matrix(cbind(primary,potential.adj))  
  K <- diag(c(rep(0,p1),rep(1,p2)))
  if(qr(primary)$rank==p1){
        bd<-det(t(x)%*%x+K/tau^2)	^(1/(p1+p2))
       #bd<-1/tr(solve(t(x)%*%solve(S)%*%x+K/tau^2))		        
	}else{
		bd<-0
	}	
  #bd <- det(t(x)%*%x + K/tau^2)^(1/(p1+p2))
  return(bd)
}
evaluateBayesianD(SSD)
```


# we assume that the first p1−1 factors are known to be active and the remaining p2 factors are to be screened
```{r}

random.row <- sample.int(2^30,10000)
#n <- 10000
index <- c(1,-1)
inf.matrix <- c()
# rep(rep(c(1,-1),each = n/2),1)
# rep(rep(c(1,-1),each = n/4),2)
#for(i in 1:n){
for(i in random.row){
  tem.matrix <- numeric(m)+1
  tem <- i
  for(j in 1:m){
    if(tem == 0){
      break
    }else{
      tem <- tem/2
      quotient <- floor(tem)
      remainder <- tem - quotient 
      tem.matrix[m-j+1] <- index[(remainder != 0)+1]
      tem <- quotient 
    }
    
  }
  
  inf.matrix <- rbind(inf.matrix, tem.matrix)
}
for(j in 1:23){
  xpri <- inf.matrix[,1:j]
  xpot <- inf.matrix[,(j+1):m]
  xpri <- cbind(1,xpri)
  #solve(t(xpri) %*% xpri) %*% t(xpri) %*% xpot
  alpha <- as.matrix(lm(xpot~xpri-1)$coefficients)
  #xpri <- cbind(1,xpri)
  R <- xpot-xpri%*%alpha
  R.range <- apply(R,2,max) - apply(R,2,min)
 #print(alpha) 
  
  tau <- sqrt(5)
  m <- ncol(SSD)
  
  #primary
  primary <- cbind(1,SSD[,1:j])
  #primary <- matrix(1,nrow = nrow(SSD),1)
  p1 <- ncol(primary)
  
  #potential
  potential <- SSD[,(j+1):m]
  #potential <- SSD
  p2 <- ncol(potential)
  potential.adj <- c()
  for(i in 1:ncol(potential)){
		xpot<-potential[,i]
		R<-xpot-primary%*%as.matrix(alpha[,i]) 
		z<-R/R.range[i]
		potential.adj<-cbind(potential.adj,z)
  }
  
  #
  x <- as.matrix(cbind(primary,potential.adj))  
  K <- diag(c(rep(0,p1),rep(1,p2)))
  for(k in 1:31){
  	if(qr(primary)$rank==p1){
          bd<-det(t(x)%*%x+K/tau^2)	^(1/(k))
  #	        bd<-1/tr(solve(t(x)%*%solve(S)%*%x+K/tau^2))		        
  	}else{
  		bd<-0
  	}	
    #bd <- det(t(x)%*%x + K/tau^2)^(1/(p1+p2))
    print(paste("first",j,",",k,"power",bd))
  }
}

 
  

```

# 
```{r}
random.row <- sample.int(2^30,10000)
#n <- 10000
index <- c(1,-1)
inf.matrix <- c()
# rep(rep(c(1,-1),each = n/2),1)
# rep(rep(c(1,-1),each = n/4),2)
#for(i in 1:n){
for(i in random.row){
  tem.matrix <- numeric(m)+1
  tem <- i
  for(j in 1:m){
    if(tem == 0){
      break
    }else{
      tem <- tem/2
      quotient <- floor(tem)
      remainder <- tem - quotient 
      tem.matrix[m-j+1] <- index[(remainder != 0)+1]
      tem <- quotient 
    }
    
  }
  
  inf.matrix <- rbind(inf.matrix, tem.matrix)
}
xpri <- cbind(1,inf.matrix)
xpot <- c()
combn.matrix <- combn(ncol(inf.matrix),2)
for(i in 1:ncol(combn.matrix)){
  xpot <- cbind(xpot, inf.matrix[,combn.matrix[1,i]] * inf.matrix[,combn.matrix[2,i]])
}

alpha <- as.matrix(lm(xpot~xpri-1)$coefficients)
#xpri <- cbind(1,xpri)
R <- xpot-xpri%*%alpha
R.range <- apply(R,2,max) - apply(R,2,min)

#primary
primary <- cbind(1,SSD)
p1 <- ncol(primary)

#potential
potential <- c()
combn.matrix <- combn(ncol(SSD),2)
for(i in 1:ncol(combn.matrix)){
  potential <- cbind(potential, SSD[,combn.matrix[1,i]] * SSD[,combn.matrix[2,i]])
}
p2 <- ncol(potential)

potential.adj <- c()
for(i in 1:ncol(potential)){
	xpot<-potential[,i]
	R<-xpot-primary%*%matrix(alpha[,i],ncol = 1) 
	z<-R/R.range[i]
	potential.adj<-cbind(potential.adj,z)
}

#
x <- as.matrix(cbind(primary,potential.adj))  
K <- diag(c(rep(0,p1),rep(1,p2)))
if(qr(primary)$rank==p1){
  bd<-det(t(x)%*%x+K/tau^2)	^(1/(p1+p2))
#	        bd<-1/tr(solve(t(x)%*%solve(S)%*%x+K/tau^2))		        
}else{
	bd<-0
}	
```


